### 2017-04-13 paper/oopsla17-submission/evaluation.tex
more notes from kamalika

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer three questions in our evaluation:
%
\begin{description}
\item[1. Blame Accuracy (\autoref{sec:quantitative})]
  %
  How often are our predictions \emph{correct}?
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item[2. Feature Utility (\autoref{sec:feature-utility})]
  %
  Which feature sets are \emph{most important} for accurate predictions?
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item[3. Explaining Predictions (\autoref{sec:qualitative})]
  %
  Can we \emph{explain} individual predictions (correct or not)?
\end{description}
%\ES{may want to swap (1) and (2)..}

@@

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
We mitigate this threat by having separate training and testing datasets
(\autoref{sec:quantitative}) and via cross-validation
(\autoref{sec:feature-utility})~\cite{FIXME}.

@@

Examining programs written in \ocaml as opposed to \haskell or any other
language poses another threat to validity, common type errors may differ
in different languages.
%
\ocaml is, however, a standard target for research in type error
localization and thus our choice admits a direct comparison with prior
work.
%
Furthermore, the functional core of \ocaml that we support does not
differ significantly from the functional core of \haskell or SML, all of
which are effectively lambda calculi with a Hindley-Milner-style type
system.\footnote{\haskell's type classes are a notable exception, they
  are also known to cause confusing type errors and would be interesting
  to study in future work.}

>>>>

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer three questions in our evaluation:
%
\begin{description}
\item[1. Blame Accuracy (\autoref{sec:quantitative})]
  %
  How often do we \emph{correctly} assign blame for the type error?
  %
  % We compare our technique with a variety of off-the-shelf classifiers
  % and find that our top-ranked blame assignments have an accuracy of
  % 72\%, compared to a state-of-the-art 56\%.
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item[2. Feature Utility (\autoref{sec:feature-utility})]
  %
  Which feature sets are \emph{most important} for accurate predictions?
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item[3. Explaining Predictions (\autoref{sec:qualitative})]
  %
  Can we \emph{explain} individual predictions (correct or not)?
\end{description}
%\ES{may want to swap (1) and (2)..}

@@

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
A similar issue that arises in machine learning is model stability (\ie
can small changes to the training set produce large changes in the model?).
%
We mitigate these threats by:
%
(1) using separate training and testing datasets drawn from distinct
student populations (\autoref{sec:quantitative}), demonstrating the
generality of our models; and
%
(2) via cross-validation on the joint dataset
(\autoref{sec:feature-utility}), which demonstrates the stability of our
models by averaging the accuracy of 10 models trained on distinct
subsets of the data.

@@

Examining programs written in \ocaml as opposed to \haskell or any other
typed functional language poses yet another threat, common type errors
may differ in different languages.
%
\ocaml is, however, a standard target for research in type error
localization and thus our choice admits a direct comparison with prior
work.
%
Furthermore, the functional core of \ocaml that we support does not
differ significantly from the functional core of \haskell or SML, all of
which are effectively lambda calculi with a Hindley-Milner-style type
system.\footnote{\haskell's type classes are a notable exception, they
  are also known to cause confusing type errors and would be interesting
  to study in future work.}
